---
title: "Aides Drug"
author: "Kayleen Sepulveda "
date: "September 28, 2021"
output: html_document
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
triUmp <-read.csv(file="triUmpsal.csv",header=TRUE)
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->

A new  preventative aides drug (triUmpsal) is under test in clinical trials. Consider only the females, does this drug seem effective?  Hint - use dplyr to obtain that subpopulation with the filter command.


$H_0$: Amoung women there is no difference in terms of percentage of women who got the vaccine and those who got the placebo.   

$H_A$: Amoung the women who contracted aids there is a difference between those who got the vaccine and those who got the placebo.  
# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->

we are using categorical~categorical helper file because all of the data is organized in categories the response variable and explanatory variable are both categorical. 


# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

```{r}
WomenData=filter(triUmp,gender=="F")
head(WomenData)
```
these are the data for all the females in the study. 

## Descriptive Results


### Graphical Descriptive Results

```{r}
barchartGC(~infected + treatment,data=WomenData)
barchartGC(~infected + treatment,data=WomenData, type="percent")

```
```{r}
dd2 <- WomenData %>% group_by(infected,treatment) %>% summarize(count=n()) %>% mutate(prcnt=count/sum(count))

basicC <- ggplot(dd2,aes(x=infected,y=count,fill=treatment))
basicC + geom_bar(stat="identity",position="dodge")
#Now for percentage plot

basicCC <- ggplot(dd2,aes(x=infected,y=prcnt*100,treatment)) 
basicCC + geom_bar(stat="identity", position = "dodge")
```


this boxplot shows that out of the women who got aids most of them had previously received the vaccine were more susceptible to contracting aids.  

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->


### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->


```{r}
table1 <- xtabs(~infected + treatment, data=WomenData)
rowPerc(table1)
colPerc(table1)
```
This Table shows that 59% of the women who contracted aids previously received the vaccine beforehand and 41% did not get the vaccine. 

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```
3 tests were ran and all the P values were far to low to accept the Null hypothesis. in a fisher exact test it indicates that the odds of a women contracting aids after receiving the vaccine is 1.543902 more likely compared to a women who may have not taken the vaccine. 

# Discussion and Conclusion

The results showed us that the odds ratio of contracting aids after getting the vaccine in women was 1.543902 : 1 the results conclude that there is a significant difference in the percentage of women who took the vaccine and those who took the placebo, thus we reject the null hypothesis. Women who got the vaccine were more likely to contract aids then those who got the placebo because the confidence interval for the odd ratio is entirely above 1; (1.240408 1.925729). The vaccine does not protect women against aids in fact it increases the chances. 

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection 

